\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{hyperref}

\setstretch{1.15}

% ---- Configurable fields ----
\newcommand{\JobTitle}{<Job Title>}
\newcommand{\Company}{<Company Name>}
\newcommand{\Manager}{<Hiring Manager's Name>}
\newcommand{\LetterDate}{<Date>}
\newcommand{\CompanyAddr}{<Company Address / Remote>}
% -----------------------------

\begin{document}

\begin{flushright}
\textbf{Sonu Kumar} \\
Email: \href{mailto:sonukumar03xt@gmail.com}{sonukumar03xt@gmail.com} \\
Phone: +91-8770617376 \\
LinkedIn: \href{https://www.linkedin.com/in/sonukumar03xt/}{linkedin.com/in/sonukumar03xt} \\
Leetcode: \href{https://leetcode.com/sonukumar03xt/}{leetcode.com/sonukumar03xt} \\
\end{flushright}

\vspace{1cm}

\noindent \LetterDate \\
\Manager \\
\Company \\
\CompanyAddr \\

\vspace{0.5cm}

\noindent Dear \Manager, \\

I am writing to express my interest in the \textbf{\JobTitle} role at \textbf{\Company}. With over four years of experience spanning full-stack and front-end engineering, I have consistently delivered impactful, user-centric solutions while mentoring teams and contributing to high-scale product development.  

At \textbf{Spotdraft}, I worked on mission-critical projects such as \emph{email customization}, \emph{summary page revamp}, and \emph{contract metadata management}, taking ownership of both front-end architecture and cross-functional collaboration. My contributions included building reusable components, improving developer tooling, reducing QA bottlenecks, and designing intuitive user experiences—ultimately enhancing product adoption and customer satisfaction. I also authored specifications, drove testing culture, and mentored new engineers, which helped scale the team’s efficiency.  

Previously at \textbf{Interbiz Consulting Pvt. Ltd.}, I served as a \textbf{Full-stack Software Engineer} where I designed complex reusable components (such as multi-level tabular UIs handling 10,000+ rows), implemented IoT polling systems using Azure Functions, and led a team of four engineers. My leadership improved team productivity by 10\% and ensured timely, reliable project delivery.  

Across these roles, I have honed expertise in \textbf{JavaScript, TypeScript, Angular, Node.js, and modern front-end architectures}, with additional backend exposure in \textbf{C\#, .NET Core, and databases like PostgreSQL/MySQL}. My recent focus includes advancing full-stack capabilities and deepening my system design knowledge to prepare for senior engineering responsibilities.  

I am particularly drawn to \textbf{\Company} because of [specific reason tailored to company/project/domain], and I am eager to bring my blend of technical depth, ownership, and collaborative mindset to help drive impactful outcomes for your team.  

Thank you for considering my application. I would welcome the opportunity to discuss how my background and skills align with the needs of \textbf{\Company}.  

\vspace{0.7cm}
\noindent Sincerely, \\
\textbf{Sonu Kumar}  

\end{document}