\documentclass[a4paper,10pt]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

% Compact bullet lists
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=0.2in}
\setcounter{secnumdepth}{0}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}[\titlerule]

\begin{document}

% ===== Header =====
\begin{center}
    {\Huge \textbf{Sonu Kumar}}\\[6pt]
    \href{mailto:sonukumar03xt@gmail.com}{sonukumar03xt@gmail.com}
    \quad|\quad (+91) 99930 4423
    \quad|\quad \href{https://www.linkedin.com/in/sonukumar03xt}{LinkedIn}
    \quad|\quad \href{https://leetcode.com/sonukumar03xt}{LeetCode}
\end{center}

\vspace{0.5em}

% ===== Work Experience =====
\section{Work Experience}

\textbf{Software Engineer | SpotDraft (Draftspotting Technologies Pvt Ltd)} \hfill Bengaluru, KA \quad \textit{Jan 2023 – Present}

\begin{itemize}
  \item \textbf{AI-augmented Development:} Leveraged AI-assisted coding and prompt engineering to accelerate feature delivery, auto-generate test cases, and enhance PR/spec reviews—boosting developer productivity and code quality.
  \item \textbf{Reusable UI Engineering:} Built core UI components (color picker, image cropper, advanced filters, popovers, campaign-like targeting components) improving user customization, engagement, and adoption.
  \item \textbf{Product-Led Growth Features:} Collaborated with PMs, designers, and backend engineers to deliver cross-sell-like components (filters, campaign workflows, notifications) similar to Ads \& Growth tooling.
  \item \textbf{High-Impact Projects:}
    \begin{itemize}
      \item Summary Page Revamp \& Metadata Side-Panel → redesigned core contract workflows, improving discoverability, usability, and retention.
      \item Review “Summary of Changes” AI Feature → led frontend across app \& Word/OnlyOffice plugins; achieved 92\% adoption.
      \item Workflow Enhancements → delivered sign field precision, approval restrictions, and advanced search filters, reducing QA tickets.
    \end{itemize}
  \item \textbf{Engineering Productivity:}
    \begin{itemize}
      \item Automated onboarding scripts → cut dev setup time from 2 days to 15 min.
      \item Refactored stateless Express → improved maintainability, reducing bug-finding time by 40\%.
      \item Optimized Angular build → reduced bundle size by 60\% and ng serve time by 80\% (via lazy loading, tree-shaking, dependency refactor).
      \item Optimized Express server with Node.js worker threads, reducing CPU-intensive document failures on-call by 80\%.
    \end{itemize}
\end{itemize}

\textit{Tech Stack: TypeScript/JavaScript, Angular, React (Draftkit), Python, Express, HTML, CSS, NxConsole, Cypress, Jest, Cursor}

\vspace{1em}

\textbf{Full-stack Software Engineer | Interbiz Consulting Pvt Ltd} \hfill Raipur, CG \quad \textit{Aug 2020 – Dec 2022}

\begin{itemize}
  \item Designed a multi-level data visualization system (nested tables + graphs) for 10k+ row datasets, enabling better insights.
  \item Built a low-latency IoT polling system using Azure Trigger \& Durable Functions.
  \item Led a team of 4 engineers—project planning, sprint execution, and daily stand-ups—improving delivery efficiency by 10\%.
  \item Mentored 12+ junior frontend developers in Angular, TypeScript, and Git, accelerating onboarding and team contribution.
  \item Maintained UI/UX consistency \& branding standards across internal apps.
\end{itemize}

\textit{Tech Stack: Angular, C\#, .NET Core, TypeScript, MySQL, Azure}

% ===== Education =====
\section{Education}
\begin{itemize}
  \item B.Tech, Information Technology – Government Engineering College, Bilaspur (2016 – 2020) | CGPA: 7.52
  \item Higher Secondary (PCM, CBSE) – Jawahar Navodaya Vidyalaya, Baikunthpur (2014 – 2016) | 86\%
\end{itemize}

% ===== Skills =====
\section{Skills}
\begin{itemize}
  \item \textbf{Languages:} JavaScript (ES6+), TypeScript, HTML, CSS
  \item \textbf{Frameworks:} React, Angular, Angular Material, Monorepo, RxJS, Cypress, Node.js, Express
  \item \textbf{Databases:} PostgreSQL, MongoDB, MySQL
  \item \textbf{Testing:} Jest, Cypress (unit, integration, e2e)
  \item \textbf{Tools:} Git, Nx Console, Jira, Docker, WOPI
  \item \textbf{AI-augmented Development:} Prompt engineering, AI-assisted test generation, AI-driven code reviews
\end{itemize}

\end{document}