\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}

\begin{document}

\noindent
\textbf{Sonu Kumar} \\
Bengaluru, KA \\
\href{mailto:sonukumar03xt@gmail.com}{sonukumar03xt@gmail.com} \,|\, (+91) 99930 44923 \\[12pt]

\noindent
[Date] \\[6pt]

\noindent
\textbf{[Hiring Manager’s Name]} \\
\textbf{[Company Name]} \\[12pt]

Dear [Hiring Manager’s Name], \\[6pt]

I am writing to express my interest in the \textbf{Frontend Engineer} position at \textbf{[Company Name]}. With over 4 years of experience in building scalable, user-centric applications, I specialize in modern frontend technologies such as Angular and React, delivering impactful UI solutions in product-led environments.

At SpotDraft, I have owned projects such as the \textbf{Summary of Changes AI feature} (92\% adoption), a complete \textbf{Summary Page Revamp}, and \textbf{email customization modules} that empower users to create branded, flexible experiences. My focus on reusable UI architecture, performance optimization, and collaboration with design and backend teams has consistently improved user experience and developer productivity.

Beyond feature delivery, I actively mentor peers, conduct thorough code reviews, and contribute to scalable component libraries. My strong foundation in frontend engineering, complemented by AI-assisted development practices, allows me to deliver high-quality solutions at speed.

I am particularly excited about contributing to \textbf{[Company Name]} because of your commitment to delivering intuitive and engaging user experiences at scale. I am confident my expertise in \textbf{UI engineering, cross-platform integration, and scalable architecture} aligns well with your team’s goals.

Thank you for considering my application. I look forward to the opportunity to discuss how I can contribute to building innovative frontend experiences at \textbf{[Company Name]}.

\\[12pt]
Sincerely, \\
\textbf{Sonu Kumar}

\end{document}