\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, left=1.5em}

\pagestyle{empty}

\begin{document}

% ---------- Header ----------
\begin{center}
    {\LARGE \textbf{Sonu Kumar}} \\[4pt]
    \href{mailto:sonukumar03xt@gmail.com}{sonukumar03xt@gmail.com} \,|\, (+91) 99930 44923 \,|\, 
    \href{https://www.linkedin.com/in/sonukumar03xt}{LinkedIn} \,|\, 
    \href{https://leetcode.com/sonukumar03xt}{LeetCode}
\end{center}

% ---------- Work Experience ----------
\section*{Work Experience}

\textbf{Software Engineer} \hfill SpotDraft (Draftspotting Technologies Pvt Ltd), Bengaluru \\
\textit{Jan 2023 -- Present}
\begin{itemize}
    \item \textbf{Frontend Ownership:} Designed and built reusable UI components (color picker, image cropper modal, advanced filters, SDK card, popovers) powering platform-wide personalization and extensibility.
    \item \textbf{Summary Page Revamp:} Owned redesign of key contract workflows (Contract Status, Approvals, Counterparty Details, Notes) and implemented a reusable data layer for overview services. Delivered 40+ bug fixes and QA improvements.
    \item \textbf{Summary of Changes (AI Feature):} Led frontend across web + Word/OnlyOffice plugins. Built change-review side sheet, reusable libraries (API/UI/Core), and seamless navigation from change summaries to document sections. Achieved \textbf{92\% adoption}.
    \item \textbf{Email Customization:} Developed base email template builder, SDK-color-picker, and integrations for workspace/entity branding; added amplitude analytics events to measure adoption.
    \item \textbf{Advanced Search Filters:} Implemented robust date filters (between, on, before/after, relative X days/weeks/months) improving reporting flexibility and insights.
    \item \textbf{Sign Page Improvements:} Added drag-and-drop placement and pixel-level arrow key precision for signature fields, drastically improving accuracy and ease of use.
    \item \textbf{Collaboration \& Mentorship:} Conducted code reviews, improved unit/e2e test coverage, worked with design, backend, and QA. Mentored new hires on frontend architecture, productivity tooling, and development workflows.
    \item \textbf{Engineering Productivity:} Automated onboarding (2 days $\rightarrow$ 15 min), optimized Angular builds (-60\% bundle size, -80\% serve time), improved Express server reliability with Node.js worker threads.
\end{itemize}

\textbf{Full-Stack Software Engineer} \hfill Interbiz Consulting Pvt Ltd, Raipur \\
\textit{Aug 2020 -- Dec 2022}
\begin{itemize}
    \item Designed and developed a multi-level data visualization system (nested tables + graphs) for datasets of 10k+ rows, used across three Angular apps.
    \item Built reusable table components for complex datasets, improving UI performance and maintainability.
    \item Mentored 12+ junior frontend developers on Angular, TypeScript, Git, and team workflows.
    \item Maintained consistent UI/UX standards across product interfaces.
\end{itemize}

% ---------- Education ----------
\section*{Education}
\textbf{B.Tech, Information Technology} \hfill Govt. Engineering College, Bilaspur \\
2016 -- 2020 \,|\, CGPA: 7.52

\textbf{Higher Secondary (PCM, CBSE)} \hfill JNV Baikunthpur \\
2014 -- 2016 \,|\, 86\%

% ---------- Skills ----------
\section*{Skills}
\begin{itemize}
    \item \textbf{Languages:} JavaScript (ES6+), TypeScript, HTML, CSS, Python (data scripting), basic C\#
    \item \textbf{Frameworks:} Angular, React, Angular Material, RxJS, Cypress, Node.js, Express
    \item \textbf{Databases:} PostgreSQL, MongoDB, MySQL
    \item \textbf{Testing:} Jest, Cypress (unit, integration, e2e)
    \item \textbf{Tools:} Git, Nx Console, Jira, Docker, WOPI
    \item \textbf{Frontend Strengths:} Scalable UI architecture, reusable component libraries, UX-focused design, cross-platform integration
    \item \textbf{AI/Dev Productivity:} Prompt engineering, AI-assisted testing, AI-driven code reviews
\end{itemize}

% ---------- Projects ----------
\section*{Projects}
\begin{itemize}
    \item \textbf{SDK-Color-Picker \& Image Cropper:} Developed reusable UI components integrated across multiple product areas, improving design consistency and developer velocity.
    \item \textbf{Summary of Changes (AI):} Built cross-platform review workflow (web + Word/OnlyOffice plugins), introducing intuitive change tracking and navigation. Rated “very helpful” by 55\% of users.
    \item \textbf{Advanced Search Filters:} Expanded search functionality with nuanced date filters (between, relative, fixed) for better reporting and insights.
    \item \textbf{Email Customization Builder:} Created a self-serve template editor allowing workspace-level branding and reducing dependency on backend configurations.
    \item \textbf{Sign Page UX Enhancements:} Delivered drag-and-drop and arrow-key precision placement for signature fields, streamlining document preparation workflows.
\end{itemize}

\end{document}