\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, left=1.5em}

\pagestyle{empty}

\begin{document}

% ---------- Header ----------
\begin{center}
    {\LARGE \textbf{Sonu Kumar}} \\[4pt]
    \href{mailto:sonukumar03xt@gmail.com}{sonukumar03xt@gmail.com} \,|\, (+91) 99930 44923 \,|\, 
    \href{https://www.linkedin.com/in/sonukumar03xt}{LinkedIn} \,|\, 
    \href{https://leetcode.com/sonukumar03xt}{LeetCode}
\end{center}

% ---------- Work Experience ----------
\section*{Work Experience}

\textbf{Software Engineer} \hfill SpotDraft (Draftspotting Technologies Pvt Ltd), Bengaluru \\
\textit{Jan 2023 -- Present}
\begin{itemize}
    \item Delivered features end-to-end across Angular/React frontends and Express/Node.js backends, collaborating with PMs, designers, and QA.
    \item Built reusable UI components (color picker, image cropper modal, advanced date filters, popovers) powering personalization and extensibility across the platform.
    \item Led major revamps including the Summary Page redesign (Contract Status, Approvals, Notes, Counterparty Details) and the Summary of Changes (AI Feature) across web + Word/OnlyOffice plugins, achieving 92\% adoption.
    \item Implemented backend validation APIs (dropdowns, signature blocks) and extended Elasticsearch logic, reducing QA tickets and enabling advanced reporting.
    \item Refactored Express services and optimized Node.js servers with worker threads, cutting CPU-intensive failures by 80\%.
    \item Automated onboarding (bash + pyenv + poetry), reducing environment setup time from 2 days $\rightarrow$ 15 minutes.
    \item Partnered with PMs, designers, and backend engineers to deliver features with polish while mentoring new hires and reviewing technical specifications.
\end{itemize}

\textbf{Full-Stack Software Engineer} \hfill Interbiz Consulting Pvt Ltd, Raipur \\
\textit{Aug 2020 -- Dec 2022}
\begin{itemize}
    \item Designed and developed multi-level data visualization systems (nested tables + graphs) for 10k+ row datasets across Angular apps.
    \item Built reusable UI table components, improving maintainability and UI performance.
    \item Developed low-latency IoT polling system using Azure Trigger \& Durable Functions.
    \item Managed a 4-person team, planned sprints, and mentored 12+ junior frontend developers.
\end{itemize}

% ---------- Education ----------
\section*{Education}
\textbf{B.Tech, Information Technology} \hfill Govt. Engineering College, Bilaspur \\
2016 -- 2020 \,|\, CGPA: 7.52

\textbf{Higher Secondary (PCM, CBSE)} \hfill JNV Baikunthpur \\
2014 -- 2016 \,|\, 86\%

% ---------- Skills ----------
\section*{Skills}
\begin{itemize}
    \item \textbf{Languages:} JavaScript (ES6+), TypeScript, HTML, CSS, Python, basic C\#
    \item \textbf{Frameworks:} Angular, React, Angular Material, RxJS, Cypress, Node.js, Express
    \item \textbf{Databases:} PostgreSQL, MongoDB, MySQL
    \item \textbf{Testing:} Jest, Cypress (unit, integration, e2e)
    \item \textbf{Tools:} Git, Nx Console, Jira, Docker, WOPI
    \item \textbf{Strengths:} End-to-end feature ownership, scalable UI architecture, API integration, developer tooling
    \item \textbf{AI/Dev Productivity:} Prompt engineering, AI-assisted testing, AI-driven code reviews
\end{itemize}

\end{document}